---
title: "NRES803"
author: "Nieto_Lopez"
date: "5/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```
## Setting the packages and wrangling

```{r set packages, echo=FALSE}

packages <- c("tidyverse","agricolae", "mosaic", "broom", "car","lawstat", "ggridges", "cowplot", "gridExtra", "arsenal", "DescTools","ezec", "lmodel2")
lapply( packages, require, character.only = TRUE)

  
```

```{r reading data}
#####boscalid  Plate dilution

boscalid.data <-
read.csv("data/boscalid.csv")
  
boscalid.data$repeats <- rep_len(1:4, length.out = nrow(boscalid.data))
boscalid.data$ID <- as.character(boscalid.data$ID)
  # renaming ID for the current names
boscalid.data$ID[ boscalid.data$ID =="541B"]  <- "541" 

boscalid.data$ID[ boscalid.data$ID =="293E"]  <- "293" 
boscalid.data$ID[ boscalid.data$ID =="973B"]  <- "973" 
boscalid.data$ID[ boscalid.data$ID =="973C"]  <- "973" 
boscalid.data$ID[ boscalid.data$ID =="973D"]  <- "973" 
boscalid.data$ID[ boscalid.data$ID =="974A"]  <- "974" 
boscalid.data$ID[ boscalid.data$ID =="974B"]  <- "974" 
boscalid.data$ID[ boscalid.data$ID =="974C"]  <- "974" 
boscalid.data$ID[ boscalid.data$ID =="974D"]  <- "974" 
boscalid.data$ID[ boscalid.data$ID =="975C"]  <- "975" 
boscalid.data$ID[ boscalid.data$ID =="975D"]  <- "975" 
boscalid.data$ID[ boscalid.data$ID =="975E"]  <- "975" 
boscalid.data$ID[ boscalid.data$ID =="976B"]  <- "976"
boscalid.data$ID[ boscalid.data$ID =="976C"]  <- "976"
boscalid.data$ID[ boscalid.data$ID =="977B"]  <- "977"
boscalid.data$ID[ boscalid.data$ID =="978B"]  <- "978"

  ####Transforming to $ID to numeric
boscalid.data$ID <- as.numeric(boscalid.data$ID)
  # Filter out 
boscalid.data <- boscalid.data %>%
     #filter(!dose ==  0.4 & !ID == 800) %>%
mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
    
#####boscalid  Spiral gradient
boscalid.SG <-
read.csv("data/1_Day_SG/Boscalid.csv")
  
boscalid.SG <- boscalid.SG %>% 
rename(ID= Isolate)
  
boscalid.SG$ID <- as.character(boscalid.SG$ID)
# renaming ID for the current names
boscalid.SG$ID[ boscalid.SG$ID =="541B"]  <- "541" 

boscalid.SG$ID[ boscalid.SG$ID =="293E"]  <- "293" 
boscalid.SG$ID[ boscalid.SG$ID =="973B"]  <- "973" 
boscalid.SG$ID[ boscalid.SG$ID =="973C"]  <- "973" 
boscalid.SG$ID[ boscalid.SG$ID =="973D"]  <- "973" 
boscalid.SG$ID[ boscalid.SG$ID =="974A"]  <- "974" 
boscalid.SG$ID[ boscalid.SG$ID =="974B"]  <- "974" 
boscalid.SG$ID[ boscalid.SG$ID =="974C"]  <- "974" 
boscalid.SG$ID[ boscalid.SG$ID =="974D"]  <- "974" 
boscalid.SG$ID[ boscalid.SG$ID =="975C"]  <- "975" 
boscalid.SG$ID[ boscalid.SG$ID =="975D"]  <- "975" 
boscalid.SG$ID[ boscalid.SG$ID =="975E"]  <- "975" 
boscalid.SG$ID[ boscalid.SG$ID =="976B"]  <- "976"
boscalid.SG$ID[ boscalid.SG$ID =="976C"]  <- "976"
boscalid.SG$ID[ boscalid.SG$ID =="977B"]  <- "977"
boscalid.SG$ID[ boscalid.SG$ID =="978B"]  <- "978"

####Transforming to $ID to numeric
boscalid.SG$ID <- as.numeric(boscalid.SG$ID)
# Filter out 
boscalid.SG <- boscalid.SG %>%
group_by(ID) %>%  
mutate(Average=mean(EC50)) %>% 
select(- EC50) %>% 
rename(EC50_SG= Average) %>% 
unique() %>% 
ungroup()
  
###Fluazinam Plate dilution
  
fluazinam.data <-
  read.csv("data/fluazinam.csv")
  
fluazinam.data$repeats <- rep_len(1:4, length.out = nrow(fluazinam.data))
fluazinam.data$ID <- as.character(fluazinam.data$ID)
  # renaming ID for the current names
fluazinam.data$ID[ fluazinam.data$ID =="541B"]  <- "541" 

fluazinam.data$ID[ fluazinam.data$ID =="293E"]  <- "293" 
fluazinam.data$ID[ fluazinam.data$ID =="973B"]  <- "973" 
fluazinam.data$ID[ fluazinam.data$ID =="973C"]  <- "973" 
fluazinam.data$ID[ fluazinam.data$ID =="973D"]  <- "973"
fluazinam.data$ID[ fluazinam.data$ID =="974A"]  <- "974" 
fluazinam.data$ID[ fluazinam.data$ID =="974B"]  <- "974" 
fluazinam.data$ID[ fluazinam.data$ID =="974C"]  <- "974" 
fluazinam.data$ID[ fluazinam.data$ID =="974D"]  <- "974" 
fluazinam.data$ID[ fluazinam.data$ID =="975C"]  <- "975" 
fluazinam.data$ID[ fluazinam.data$ID =="975D"]  <- "975" 
fluazinam.data$ID[ fluazinam.data$ID =="975E"]  <- "975" 
fluazinam.data$ID[ fluazinam.data$ID =="976B"]  <- "976"
fluazinam.data$ID[ fluazinam.data$ID =="976C"]  <- "976"
fluazinam.data$ID[ fluazinam.data$ID =="977B"]  <- "977"
fluazinam.data$ID[ fluazinam.data$ID =="978B"]  <- "978"

 
####Transforming to $ID to numeric
fluazinam.data$ID <- as.numeric(fluazinam.data$ID)
# Filter out 
fluazinam.data <- fluazinam.data %>%
mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
 

  ###Fluazinam Spiral Gradient
fluazinam.SG <-
read.csv("data/1_Day_SG/Fluazinam.csv")
  
fluazinam.SG <- fluazinam.SG %>% 
rename(ID= Isolate)
  
fluazinam.SG$ID <- as.character(fluazinam.SG$ID)
# renaming ID for the current names
fluazinam.SG$ID[ fluazinam.SG$ID =="541B"]  <- "541" 

fluazinam.SG$ID[ fluazinam.SG$ID =="293E"]  <- "293" 
fluazinam.SG$ID[ fluazinam.SG$ID =="973B"]  <- "973" 
fluazinam.SG$ID[ fluazinam.SG$ID =="973C"]  <- "973" 
fluazinam.SG$ID[ fluazinam.SG$ID =="973D"]  <- "973" 
fluazinam.SG$ID[ fluazinam.SG$ID =="974A"]  <- "974" 
fluazinam.SG$ID[ fluazinam.SG$ID =="974B"]  <- "974" 
fluazinam.SG$ID[ fluazinam.SG$ID =="974C"]  <- "974" 
fluazinam.SG$ID[ fluazinam.SG$ID =="974D"]  <- "974" 
fluazinam.SG$ID[ fluazinam.SG$ID =="975C"]  <- "975" 
fluazinam.SG$ID[ fluazinam.SG$ID =="975D"]  <- "975" 
fluazinam.SG$ID[ fluazinam.SG$ID =="975E"]  <- "975" 
fluazinam.SG$ID[ fluazinam.SG$ID =="976B"]  <- "976"
fluazinam.SG$ID[ fluazinam.SG$ID =="976C"]  <- "976"
fluazinam.SG$ID[ fluazinam.SG$ID =="977B"]  <- "977"
fluazinam.SG$ID[ fluazinam.SG$ID =="978B"]  <- "978"

 
####Transforming to $ID to numeric
fluazinam.SG$ID <- as.numeric(fluazinam.SG$ID)
# Filter out 
fluazinam.SG <- fluazinam.SG %>%
group_by(ID) %>%  
mutate(Average=mean(EC50)) %>% 
select(- EC50) %>% 
rename(EC50_SG= Average) %>% 
unique() %>% 
ungroup()


  
#######Iprodione Plate dilution

iprodione.data <-
read.csv("data/iprodione.csv")
  
iprodione.data$repeats <- rep_len(1:4, length.out = nrow(iprodione.data))
iprodione.data$ID <- as.character(iprodione.data$ID)
# renaming ID for the current names
iprodione.data$ID[ iprodione.data$ID =="541B"]  <- "541" 

iprodione.data$ID[ iprodione.data$ID =="293E"]  <- "293" 
iprodione.data$ID[ iprodione.data$ID =="973B"]  <- "973" 
iprodione.data$ID[ iprodione.data$ID =="973C"]  <- "973" 
iprodione.data$ID[ iprodione.data$ID =="973D"]  <- "973"
iprodione.data$ID[ iprodione.data$ID =="974A"]  <- "974" 
iprodione.data$ID[ iprodione.data$ID =="974B"]  <- "974" 
iprodione.data$ID[ iprodione.data$ID =="974C"]  <- "974" 
iprodione.data$ID[ iprodione.data$ID =="974D"]  <- "974" 
iprodione.data$ID[ iprodione.data$ID =="975C"]  <- "975" 
iprodione.data$ID[ iprodione.data$ID =="975D"]  <- "975" 
iprodione.data$ID[ iprodione.data$ID =="975E"]  <- "975" 
iprodione.data$ID[ iprodione.data$ID =="976B"]  <- "976"
iprodione.data$ID[ iprodione.data$ID =="976C"]  <- "976"
iprodione.data$ID[ iprodione.data$ID =="977B"]  <- "977"
iprodione.data$ID[ iprodione.data$ID =="978B"]  <- "978"

 
####Transforming to $ID to numeric
iprodione.data$ID <- as.numeric(iprodione.data$ID)
# Filter out 
iprodione.data <- iprodione.data %>%
mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
    
 ###Iprodione Spiral Gradient
iprodione.SG <-
read.csv("data/1_Day_SG/Iprodione.csv")
  
iprodione.SG <- iprodione.SG %>% 
rename(ID= Isolate)
  
iprodione.SG$ID <- as.character(iprodione.SG$ID)
# renaming ID for the current names
iprodione.SG$ID[ iprodione.SG$ID =="541B"]  <- "541" 

iprodione.SG$ID[ iprodione.SG$ID =="293E"]  <- "293" 
iprodione.SG$ID[ iprodione.SG$ID =="973B"]  <- "973" 
iprodione.SG$ID[ iprodione.SG$ID =="973C"]  <- "973" 
iprodione.SG$ID[ iprodione.SG$ID =="973D"]  <- "973" 
iprodione.SG$ID[ iprodione.SG$ID =="974A"]  <- "974" 
iprodione.SG$ID[ iprodione.SG$ID =="974B"]  <- "974" 
iprodione.SG$ID[ iprodione.SG$ID =="974C"]  <- "974" 
iprodione.SG$ID[ iprodione.SG$ID =="974D"]  <- "974" 
iprodione.SG$ID[ iprodione.SG$ID =="975C"]  <- "975" 
iprodione.SG$ID[ iprodione.SG$ID =="975D"]  <- "975" 
iprodione.SG$ID[ iprodione.SG$ID =="975E"]  <- "975" 
iprodione.SG$ID[ iprodione.SG$ID =="976B"]  <- "976"
iprodione.SG$ID[ iprodione.SG$ID =="976C"]  <- "976"
iprodione.SG$ID[ iprodione.SG$ID =="977B"]  <- "977"
iprodione.SG$ID[ iprodione.SG$ID =="978B"]  <- "978"

 
 ####Transforming to $ID to numeric
 iprodione.SG$ID <- as.numeric(iprodione.SG$ID)
 # Filter out 
 iprodione.SG <- iprodione.SG %>%
 group_by(ID) %>%  
 mutate(Average=mean(EC50)) %>% 
 select(- EC50) %>% 
 rename(EC50_SG= Average) %>% 
 unique() %>% 
ungroup()
  
    
  
###Procymidone Plate dilution
  
procymidone.data <-
read.csv("data/procymidone.csv")
  
procymidone.data$repeats <- rep_len(1:4, length.out = nrow(procymidone.data))
procymidone.data$ID <- as.character(procymidone.data$ID)
  # renaming ID for the current names
procymidone.data$ID[ procymidone.data$ID =="541B"]  <- "541" 

procymidone.data$ID[ procymidone.data$ID =="293E"]  <- "293" 
procymidone.data$ID[ procymidone.data$ID =="973B"]  <- "973" 
procymidone.data$ID[ procymidone.data$ID =="973C"]  <- "973" 
procymidone.data$ID[ procymidone.data$ID =="973D"]  <- "973" 
procymidone.data$ID[ procymidone.data$ID =="974A"]  <- "974" 
procymidone.data$ID[ procymidone.data$ID =="974B"]  <- "974" 
procymidone.data$ID[ procymidone.data$ID =="974C"]  <- "974" 
procymidone.data$ID[ procymidone.data$ID =="974D"]  <- "974" 
procymidone.data$ID[ procymidone.data$ID =="975C"]  <- "975" 
procymidone.data$ID[ procymidone.data$ID =="975D"]  <- "975" 
procymidone.data$ID[ procymidone.data$ID =="975E"]  <- "975" 
procymidone.data$ID[ procymidone.data$ID =="976B"]  <- "976"
procymidone.data$ID[ procymidone.data$ID =="976C"]  <- "976"
procymidone.data$ID[ procymidone.data$ID =="977B"]  <- "977"
procymidone.data$ID[ procymidone.data$ID =="978B"]  <- "978"


 ####Transforming to $ID to numeric
 procymidone.data$ID <- as.numeric(procymidone.data$ID)
 # Filter out 
 procymidone.data <- procymidone.data %>%
 #filter(!dose ==  0.4 & !ID == 800) %>%
 mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
  
  ###Procymidone Spiral Gradient
 procymidone.SG <-
 read.csv("data/1_Day_SG/Procymidone.csv")
  
 procymidone.SG <- procymidone.SG %>% 
 rename(ID= Isolate)
  
 procymidone.SG$ID <- as.character(procymidone.SG$ID)
 # renaming ID for the current names
 procymidone.SG$ID[ procymidone.SG$ID =="541B"]  <- "541" 

 procymidone.SG$ID[ procymidone.SG$ID =="293E"]  <- "293" 
 procymidone.SG$ID[ procymidone.SG$ID =="973B"]  <- "973" 
 procymidone.SG$ID[ procymidone.SG$ID =="973C"]  <- "973" 
 procymidone.SG$ID[ procymidone.SG$ID =="973D"]  <- "973" 
 procymidone.SG$ID[ procymidone.SG$ID =="974A"]  <- "974" 
 procymidone.SG$ID[ procymidone.SG$ID =="974B"]  <- "974" 
 procymidone.SG$ID[ procymidone.SG$ID =="974C"]  <- "974" 
 procymidone.SG$ID[ procymidone.SG$ID =="974D"]  <- "974" 
 procymidone.SG$ID[ procymidone.SG$ID =="975C"]  <- "975" 
 procymidone.SG$ID[ procymidone.SG$ID =="975D"]  <- "975" 
 procymidone.SG$ID[ procymidone.SG$ID =="975E"]  <- "975" 
 procymidone.SG$ID[ procymidone.SG$ID =="976B"]  <- "976"
 procymidone.SG$ID[ procymidone.SG$ID =="976C"]  <- "976"
 procymidone.SG$ID[ procymidone.SG$ID =="977B"]  <- "977"
 procymidone.SG$ID[ procymidone.SG$ID =="978B"]  <- "978"

 
 ####Transforming to $ID to numeric
 procymidone.SG$ID <- as.numeric(procymidone.SG$ID)
  # Filter out 
 procymidone.SG <- procymidone.SG %>%
 group_by(ID) %>%  
 mutate(Average=mean(EC50)) %>% 
 select(- EC50) %>% 
 rename(EC50_SG= Average) %>% 
 unique() %>% 
 ungroup()
    
  
  ###Prothioconazole Plate dilution
  prothioconazole.data <-
  read.csv("data/prothioconazole.csv")
  
prothioconazole.data$repeats <- rep_len(1:4, length.out = nrow(prothioconazole.data))
prothioconazole.data$ID <- as.character(prothioconazole.data$ID)
# renaming ID for the current names
prothioconazole.data$ID[ prothioconazole.data$ID =="541B"]  <- "541" 

prothioconazole.data$ID[ prothioconazole.data$ID =="293E"]  <- "293" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="973B"]  <- "973" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="973C"]  <- "973"
 prothioconazole.data$ID[ prothioconazole.data$ID =="973D"]  <- "973"
 prothioconazole.data$ID[ prothioconazole.data$ID =="974A"]  <- "974" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="974B"]  <- "974" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="974C"]  <- "974" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="974D"]  <- "974" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="975C"]  <- "975" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="975D"]  <- "975" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="975E"]  <- "975" 
 prothioconazole.data$ID[ prothioconazole.data$ID =="976B"]  <- "976"
 prothioconazole.data$ID[ prothioconazole.data$ID =="976C"]  <- "976"
 prothioconazole.data$ID[ prothioconazole.data$ID =="977B"]  <- "977"
 prothioconazole.data$ID[ prothioconazole.data$ID =="978B"]  <- "978"

 
####Transforming to $ID to numeric
prothioconazole.data$ID <- as.numeric(prothioconazole.data$ID)
# Filter out 
prothioconazole.data <- prothioconazole.data %>%

    mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
    
###Prothioconazole Spiral Gradient
prothioconazole.SG <-
read.csv("data/1_Day_SG/Prothioconazole.csv")
  
prothioconazole.SG <- prothioconazole.SG %>% 
rename(ID= Isolate)
  
prothioconazole.SG$ID <- as.character(prothioconazole.SG$ID)
# renaming ID for the current names
prothioconazole.SG$ID[ prothioconazole.SG$ID =="541B"]  <- "541" 

prothioconazole.SG$ID[ prothioconazole.SG$ID =="293E"]  <- "293" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="973B"]  <- "973" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="973C"]  <- "973" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="973D"]  <- "973" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="974A"]  <- "974" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="974B"]  <- "974" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="974C"]  <- "974" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="974D"]  <- "974" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="975C"]  <- "975" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="975D"]  <- "975" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="975E"]  <- "975" 
prothioconazole.SG$ID[ prothioconazole.SG$ID =="976B"]  <- "976"
prothioconazole.SG$ID[ prothioconazole.SG$ID =="976C"]  <- "976"
prothioconazole.SG$ID[ prothioconazole.SG$ID =="977B"]  <- "977"
prothioconazole.SG$ID[prothioconazole.SG$ID == "978B"]  <- "978"

 
####Transforming to $ID to numeric
prothioconazole.SG$ID <- as.numeric(prothioconazole.SG$ID)
# Filter out
prothioconazole.SG <- prothioconazole.SG %>%
group_by(ID) %>%
mutate(Average = mean(EC50)) %>%
select(-EC50) %>%
rename(EC50_SG = Average) %>%
unique() %>%
ungroup()

##pyraclostrobin Plate dilution
pyraclostrobin.data <-
read.csv("data/pyraclostrobin.csv")

pyraclostrobin.data$repeats <-
rep_len(1:4, length.out = nrow(pyraclostrobin.data))
pyraclostrobin.data$ID <- as.character(pyraclostrobin.data$ID)
# renaming ID for the current names
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "541B"]  <- "541"

pyraclostrobin.data$ID[pyraclostrobin.data$ID == "293E"]  <- "293"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "973B"]  <- "973"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "973C"]  <- "973"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "973D"]  <- "973"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "974A"]  <- "974"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "974B"]  <- "974"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "974C"]  <- "974"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "974D"]  <- "974"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "975C"]  <- "975"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "975D"]  <- "975"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "975E"]  <- "975"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "976B"]  <- "976"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "976C"]  <- "976"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "977B"]  <- "977"
pyraclostrobin.data$ID[pyraclostrobin.data$ID == "978B"]  <- "978"
####Transforming to $ID to numeric
pyraclostrobin.data$ID <- as.numeric(pyraclostrobin.data$ID)
# Filter out
pyraclostrobin.data <- pyraclostrobin.data %>%
#filter(!dose ==  0.4 & !ID == 800) %>%
mutate(response = replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6


#Pyraclostrobin Serial dilution
pyraclostrobin.SG <-
read.csv("data/1_Day_SG/Pyraclostrobin.csv")

##Pyraclostrobin Spiral Gradient
pyraclostrobin.SG <- pyraclostrobin.SG %>%
rename(ID = Isolate)

pyraclostrobin.SG$ID <- as.character(pyraclostrobin.SG$ID)
# renaming ID for the current names
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "541B"]  <- "541"

pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "293E"]  <- "293"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "973B"]  <- "973"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "973C"]  <- "973"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "973D"]  <- "973"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "974A"]  <- "974"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "974B"]  <- "974"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "974C"]  <- "974"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "974D"]  <- "974"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "975C"]  <- "975"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "975D"]  <- "975"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "975E"]  <- "975"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "976B"]  <- "976"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "976C"]  <- "976"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "977B"]  <- "977"
pyraclostrobin.SG$ID[pyraclostrobin.SG$ID == "978B"]  <- "978"


####Transforming to $ID to numeric
pyraclostrobin.SG$ID <- as.numeric(pyraclostrobin.SG$ID)
# Filter out
pyraclostrobin.SG <- pyraclostrobin.SG %>%
group_by(ID) %>%
mutate(Average = mean(EC50)) %>%
select(-EC50) %>%
rename(EC50_SG = Average) %>%
unique() %>%
ungroup()

#thiophanate_methyl Plate dilution
  
thiophanate_methyl.data <-
  read.csv("data/thiophanate_methyl.csv")
  
  thiophanate_methyl.data$repeats <-
  rep_len(1:4, length.out = nrow(thiophanate_methyl.data))
  thiophanate_methyl.data$ID <-
  as.character(thiophanate_methyl.data$ID)
  # renaming ID for the current names
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "541B"]  <-
  "541"
  
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "293E"]  <-
  "293"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "973B"]  <-
  "973"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "973C"]  <-
  "973"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "973D"]  <-
  "973"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "974A"]  <-
  "974"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "974B"]  <-
  "974"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "974C"]  <-
  "974"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "974D"]  <-
  "974"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "975C"]  <-
  "975"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "975D"]  <-
  "975"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "975E"]  <-
  "975"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "976B"]  <-
  "976"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "976C"]  <-
  "976"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "977B"]  <-
  "977"
  thiophanate_methyl.data$ID[thiophanate_methyl.data$ID == "978B"]  <-
  "978"
  
  ####Transforming to $ID to numeric
  thiophanate_methyl.data$ID <- as.numeric(thiophanate_methyl.data$ID)
  # Filter out
  #thiophanate_methyl.data <- thiophanate_methyl.data %>%
  
  # mutate(response= replace(response, response == 0, 0.6))  #replacing 0 cm growth for the size of plug that is 0.6
  
  ##Thiophanate_methyl Spiral Gradient
  thiophanate_methyl.SG <-
  read.csv("data/1_Day_SG/Thiophanate_methyl.csv",  na.strings = TRUE)
  
  thiophanate_methyl.SG <- thiophanate_methyl.SG %>%
  rename(ID = Isolate)
  
  thiophanate_methyl.SG$ID <- as.character(thiophanate_methyl.SG$ID)
  # renaming ID for the current names
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "541B"]  <-
  "541"
  
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "293E"]  <-
  "293"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "973B"]  <-
  "973"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "973C"]  <-
  "973"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "973D"]  <-
  "973"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "974A"]  <-
  "974"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "974B"]  <-
  "974"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "974C"]  <-
  "974"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "974D"]  <-
  "974"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "975C"]  <-
  "975"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "975D"]  <-
  "975"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "975E"]  <-
  "975"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "976B"]  <-
  "976"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "976C"]  <-
  "976"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "977B"]  <-
  "977"
  thiophanate_methyl.SG$ID[thiophanate_methyl.SG$ID == "978B"]  <-
  "978"
  
  
  ####Transforming to $ID to numeric
  thiophanate_methyl.SG$ID <- as.numeric(thiophanate_methyl.SG$ID)
  # Filter out
  thiophanate_methyl.SG <- thiophanate_methyl.SG %>%
  group_by(ID) %>%
  mutate(Average = mean(EC50)) %>%
  select(-EC50) %>%
  rename(EC50_SG = Average) %>%
  unique() %>%
  ungroup()
  
```

```{r}
#Function to detect ouliers among observations within same isolate and dose and take them away

get_range <- function(mynumber) {
  bb <- boxplot.stats(mynumber)
  cc <- bb$stats
  dd <- max(cc)
  ee <- min(cc)
  return(data.frame(upper = dd, lower = ee))
}
```
# Determination of EC50 by Dose-response curve by package "ezec" using ) using the “LL.3” model implemented in the R “drc” package 
```{r}
#Boscalid
boscalid.filtered <- boscalid.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  aa <- EC_table(boscalid.filtered, form = response ~ dose)
  
  boscalid.PD <-
  aa %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  boscalid.final <- boscalid.PD %>%
  left_join(boscalid.SG)
  
  #Fluazinam
  fluazinam.filtered <- fluazinam.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  bb <- EC_table(fluazinam.filtered, form = response ~ dose)
  
  fluazinam.PD <-
  bb %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  fluazinam.final <- fluazinam.PD %>%
  left_join(fluazinam.SG)
  
  #Iprodione
  iprodione.filtered <- iprodione.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  cc <- EC_table(iprodione.filtered, form = response ~ dose)
  
  iprodione.PD <-
  cc %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  iprodione.final <- iprodione.PD %>%
  left_join(iprodione.SG)
  #Procymidone
  procymidone.filtered <- procymidone.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  dd <- EC_table(procymidone.filtered, form = response ~ dose)
  
  procymidone.PD <-
  dd %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  procymidone.final <- procymidone.PD %>%
  left_join(procymidone.SG)
  #Prothioonazole
  prothioconazole.filtered <- prothioconazole.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  ee <- EC_table(prothioconazole.filtered, form = response ~ dose)
  
  prothioconazole.PD <-
  ee %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  prothioconazole.final <- prothioconazole.PD %>%
  left_join(prothioconazole.SG)
  
  #Pyraclostrobin
    pyraclostrobin.filtered <- pyraclostrobin.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  ff <- EC_table(pyraclostrobin.filtered, form = response ~ dose)
  
  pyraclostrobin.PD <-
  ff %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  pyraclostrobin.final <- pyraclostrobin.PD %>%
  left_join(pyraclostrobin.SG)
  
  #Thiophanate methyl
  thiophanate_methyl.filtered <- thiophanate_methyl.data %>%
  group_by(ID, dose) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower) %>%
  ungroup() %>%
  select(c(ID, dose, response, repeats))
  
  gg <- EC_table(thiophanate_methyl.filtered, form = response ~ dose)
  
  thiophanate_methyl.PD <-
  gg %>% rename(ID = sample) %>% # renaming
  rename(EC50_PD = Estimate.50) %>%
  select(ID, EC50_PD)
  
  #Unfortunately Spiral gradient just release the EC50 average per isolate and no any model is provided
  thiophanate_methyl.final <- thiophanate_methyl.PD %>%
  left_join(thiophanate_methyl.SG)
  
```

It was suggested by Dr Drew Tyre, follow two possible choices:
-Type II regression model
-Fit a single dose response model to all the data,including the type of assay as a covariate on one or more of the parameters in the model. However, the spiral plater inject the fungicide in the petri plate as spiral way from the highest concentration (center) to the lowest (edges) and then we set should set the growth in comparison with a control,  in a special software (spiral plater software) and it delivers the EC50, so the measurements in cm (growth) are completely different from SG and AD. So then I am lack of more covariates.

For that reason I will go for the Type II regression model which of the main difference with the type I is that X variable is the INDEPENDENT  and Y is the DEPENDENT variable. It assumes little or no error in X and all regression error is attributed to measurement or other error in Y. Meanwhile, Type II regression model which of neither X nor Y is an INDEPENDENT variable but both are assumed to be DEPENDENT on some other parameter which is often unknown. So, then both include some error.

Anyways I will try first the linear model regression type I
```{r}
# Boscalid
boscalid.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data =  boscalid.final)
summary(boscalid.model.1)

boscalid.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data =  boscalid.final[-c(19, 21, 22), ])
  summary(boscalid.model.1)
  
  
  tidy(boscalid.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(boscalid.model.1)
  # the standarized residuals seem to be normal distributed, an assumption of the linear model. The variance seems somewhat homgoneous but not completely. There are 3 observations which have high impact in in the standirezd resdiduals & in leverage and in cook distance, respectively. It would be right to take them out.
  
  boscalid.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data =  boscalid.final[-c(19, 21, 22), ])
  summary(boscalid.model.1)
  
  tidy(boscalid.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(boscalid.model.1)
  
  # According to the R2, the proportion of the variation of  Y explained by  x is 0.27 or 27% which is low  
  
  ##Fluazinam
  fluazinam.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = fluazinam.final)
  summary(fluazinam.model.1)
  
  tidy( fluazinam.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(fluazinam.model.1)
  
  # the standarized residuals seem to be not normal distributed, a lack of assumption of the linear model. The variance seems somewhat homgoneous but not completely. According to the R2, the proportion of the variation of  Y explained by  x is 0.0185 or 1.8% which is too low! 
  
  ##Iprodione
  iprodione.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = iprodione.final)
  summary(iprodione.model.1)
  
  # the standarized residuals seem to be not normal distributed, a lack of assumption of the linear model. The variance seems somewhat homgoneous but not completely. According to the R2, the proportion of the variation of  Y explained by  x is 0.03367 or 3.3% which is very low!
   tidy(iprodione.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(iprodione.model.1)
  
  ##Procymidone
  procymidone.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = procymidone.final)
  summary(procymidone.model.1)
  # the standarized residuals seem to be not normal distributed, a lack of assumption of the linear model. The variance seems somewhat homgoneous but not completely. According to the R2, the proportion of the variation of  Y explained by  x is 0.00175 or 1.7.% which is very low!
   tidy(procymidone.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(procymidone.model.1)
  
  ##Prothioconazole
  prothioconazole.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = prothioconazole.final)
  summary(prothioconazole.model.1)
  # the standarized residuals seem to be not normal distributed, a lack of assumption of the linear model. The variance seems somewhat homgoneous but not completely. According to the R2, the proportion of the variation of  Y explained by  x is 0.4792 or 47.92% which is low! There are 2 observations which have high impact in the residuals. It would be right to take them out.
  tidy(prothioconazole.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(prothioconazole.model.1)
  
  
  prothioconazole.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = prothioconazole.final[-c(6, 10), ])
  summary(prothioconazole.model.1)
  plot(prothioconazole.model.1)
  
 # Now   and according to the R2, the proportion of the variation of  Y explained by  x is 0.5827 or 58.27% which is somewhat low
 
   ##Pyraclostrobin
  pyraclostrobin.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = pyraclostrobin.final)
  summary(pyraclostrobin.model.1)
  
  tidy( pyraclostrobin.model.1, conf.int = TRUE)
  old.par = par(mfrow = c(2, 2))
  plot(pyraclostrobin.model.1)
  
  # the standarized residuals seem to be normal distributed, an assumption of the linear model. The variance seems somewhat homgoneous but not completely. There are 3 observations which have high impact in in the standirezd resdiduals & in leverage and in cook distance, respectively. It would be right to take them out.
  pyraclostrobin.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = pyraclostrobin.final[-c(15, 21, 23), ])
  summary(pyraclostrobin.model.1)
  
  # Even though the R2, the proportion of the variation of  Y explained by  x is 0.1633 or 16.33% which is very low
  
  #Thiophanate_methyl
  thiophanate_methyl.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data = thiophanate_methyl.final)
  summary(thiophanate_methyl.model.1)
  
  tidy(  thiophanate_methyl.model.1, conf.int = TRUE)
  
  old.par = par(mfrow = c(2, 2))
  plot(thiophanate_methyl.model.1)
  # the standarized residuals seem to be normal distributed, an assumption of the linear model. The variance seems somewhat homgoneous but not completely. There are 3 observations which have high impact in in the standirezd resdiduals. It would be right to take them out. Even though the R2, the proportion of the variation of  Y explained by  x is 0.1672 or 16.72% which is very low
  
   thiophanate_methyl.model.1 <-
  lm(log(EC50_PD) ~ log(EC50_SG), data =  thiophanate_methyl.final[-c(5, 21, 25), ])
   summary(thiophanate_methyl.model.1)
```

```{r}
#Boscalid
boscalid.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = boscalid.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(boscalid.model.2)
plot(boscalid.model.2)
plot(boscalid.model.2,"RMA")
plot(boscalid.model.2,"OLS")
plot(boscalid.model.2,"SMA")

#Fluazinam
fluazinam.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = fluazinam.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(fluazinam.model.2)
plot(fluazinam.model.2)
plot(fluazinam.model.2,"RMA")
plot(fluazinam.model.2,"OLS")
plot(fluazinam.model.2,"SMA")

#Iprodione
iprodione.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = iprodione.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(iprodione.model.2)
plot(iprodione.model.2)
plot(iprodione.model.2,"RMA")
plot(iprodione.model.2,"OLS")
plot(iprodione.model.2,"SMA")
#Procymidone
procymidone.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = procymidone.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(procymidone.model.2)
plot(procymidone.model.2)
plot(procymidone.model.2,"RMA")
plot(procymidone.model.2,"OLS")
plot(procymidone.model.2,"SMA")
#Prothioconazole
prothioconazole.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = prothioconazole.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(prothioconazole.model.2)
plot(prothioconazole.model.2)
plot(prothioconazole.model.2,"RMA")
plot(prothioconazole.model.2,"OLS")
plot(prothioconazole.model.2,"SMA")
#Pyraclostrobin
pyraclostrobin.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = pyraclostrobin.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(pyraclostrobin.model.2)
plot(pyraclostrobin.model.2)
plot(pyraclostrobin.model.2,"RMA")
plot(pyraclostrobin.model.2,"OLS")
plot(pyraclostrobin.model.2,"SMA")
#Thiophanate_methyl
thiophanate_methyl.model.2 <-
  lmodel2(log(EC50_PD) ~ log(EC50_SG),
  data = thiophanate_methyl.final, range.y = "interval", range.x = "interval",nperm = 99)
  summary(thiophanate_methyl.model.2)
plot(thiophanate_methyl.model.2)
plot(thiophanate_methyl.model.2,"RMA")
plot(thiophanate_methyl.model.2,"OLS")
plot(thiophanate_methyl.model.2,"SMA")


```



```{r}
####
plug.discs <-
  read.csv(
  "data/Paper_discs_vs_PLUG.csv",
  stringsAsFactors = TRUE,
  na.strings = TRUE
  )
  plug.discs$Fungicide <- str_squish(plug.discs$Fungicide)
  stopifnot(nrow(plug.discs) == 7 * 11 * 2 * 2 * 2 * 4)
  #Y <- read.csv("data/Paper_discs_vs_PLUG.csv", stringsAsFactors = TRUE, na.strings = TRUE)
  
  #stopifnot(nrow(plugdiscs)== 7*11*2*2*2*4)
  plug.discs <- plug.discs %>%
  mutate(inoculum = as.character(inoculum)) %>%
  rename(ID = inoculum,
  experimental_replicate = experimental_repetition) %>%
  select(Fungicide,
  ID,
  experiment,
  experimental_replicate,
  treatment,
  growth) %>%
  group_by(Fungicide, ID, experiment, experimental_replicate, treatment) %>% mutate(rep = 1:4) %>% spread(treatment, growth) %>%
  ungroup()
  # group_by(ID, experiment, experimental_repeatlicate)
  #spread( treatment )
```

##  By fungicide
## prothioconazole
```{r prothioconazole}

#prothioconazole
prothioconazole.plug.discs <-
plug.discs %>% filter(Fungicide == "prothioconazole") %>%
rename(response = fungicide) %>%
select(-Fungicide)

prothioconazole.plug.discs.filtered <-
prothioconazole.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
prothioconazole.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))

# transforming to log
prothioconazole.plug.discs.filtered.2 <-
prothioconazole.plug.discs.filtered %>%
mutate(log.inhibition = log(inhibition))
###
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
prothioconazole.plug.discs.filtered.2 %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$log.inhibition)))


prothioconazole.1 <- lm()

#non parametric between experimental repeatlicates and experiment, there is differenc between experiment and experimental replicates, so I cant join data from experimental replicates
prothioconazole.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experimental_replicate,
data = .)


prothioconazole.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experiment,
data = .)

# Now Dunn test

prothioconazole.plug.discs.filtered  %>% DunnTest(inhibition ~ experiment, data = ., method = "bonferroni")
#P VALUE 0.000016 *** plug-paper

```
## Fluazinam
```{r Fluazinam}
#Fluazinam
fluazinam.plug.discs <-
plug.discs %>% filter(Fungicide == "fluazinam") %>%
rename(response = fungicide) %>%
select(-Fungicide)

fluazinam.plug.discs.filtered <-  fluazinam.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There is normality between experimental replicates
fluazinam.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))

#ANOVA between experimental repeatlicates and experiment, there is difference between experiment and experimental replicates, so I cant join data from experimental replicates

fluazinam.plug.discs.filtered  %>%
aov(inhibition ~ experiment  + experimental_replicate,
data = .) %>%
summary()

```
## Iprodione
```{r Iprodione}


iprodione.plug.discs <-
plug.discs %>% filter(Fungicide == "iprodione") %>%
rename(response = fungicide) %>%
select(-Fungicide)

iprodione.plug.discs.filtered <-  iprodione.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There is normality in one exp replicate but not in the other one
iprodione.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))


# transforming to log
iprodione.plug.discs.filtered.2 <-
iprodione.plug.discs.filtered %>%
mutate(log.inhibition = log(inhibition))
###
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
iprodione.plug.discs.filtered.2 %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$log.inhibition)))


#non parametric test between experimental repeatlicates and experiment, there is differenc between experiment and experimental replicates, so I cant join data from experimental replicates

iprodione.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experimental_replicate,
data = .)


iprodione.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experiment,
data = .)

# Now Dunn test

iprodione.plug.discs.filtered  %>% DunnTest(inhibition ~ experiment, data = ., method = "bonferroni")
#P VALUE 0.0258 *plug-paper

```
## Procymidone
```{r Procymidone}


procymidone.plug.discs <-
plug.discs %>% filter(Fungicide == "procymidone") %>%
rename(response = fungicide) %>%
select(-Fungicide)

procymidone.plug.discs.filtered <-  procymidone.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There is normality in one experimental replicate but not in the other one
procymidone.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))

# transforming to square
procymidone.plug.discs.filtered.2 <-
procymidone.plug.discs.filtered %>%
mutate(square.inhibition = inhibition ^ 2)
###
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
procymidone.plug.discs.filtered.2 %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$square.inhibition)))


# non parametric test between experimental repeatlicates and experiment, there is differenc between  experimental replicates (so I cant join data from experimental) but not  between experiments

procymidone.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experimental_replicate,
data = .)


procymidone.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experiment,
data = .)
#p value = 0.09274


```

## Prothioconazole
```{r Prothioconazole}
## Prothioconazole
prothioconazole.plug.discs <-
plug.discs %>% filter(Fungicide == "prothioconazole") %>%
rename(response = fungicide) %>%
select(-Fungicide)

prothioconazole.plug.discs.filtered <-
prothioconazole.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
prothioconazole.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))

# transforming to log
prothioconazole.plug.discs.filtered.2 <-
prothioconazole.plug.discs.filtered %>%
mutate(log.inhibition = log(inhibition))
###
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
prothioconazole.plug.discs.filtered.2 %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$log.inhibition)))


# non parametric test between experimental repeatlicates and experiment, there is no difference between experiment and  experimental replicates, so I can join data from experimental replicates

prothioconazole.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experimental_replicate,
data = .)


prothioconazole.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experiment,
data = .)

```
## Pyraclostrobin
```{r Pyraclostrobin}
## Pyraclostrobin
pyraclostrobin.plug.discs <-
plug.discs %>% filter(Fungicide == "pyraclostrobin") %>%
rename(response = fungicide) %>%
select(-Fungicide)

pyraclostrobin.plug.discs.filtered <-  pyraclostrobin.plug.discs %>%
group_by(ID, experiment) %>%
mutate(response_range = list(get_range(response))) %>%
unnest() %>%
mutate(control_range = list(get_range(control))) %>%
unnest() %>%
filter(response <= upper &
response >= lower,
control <= upper1 & control >= lower1) %>%
ungroup() %>%
select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%

# Percent inhibition is (control - funcide) / (control)
mutate(inhibition = 100 * ((control - response) / control)) %>%
#taking again outliers based on inhibition
group_by(ID, experiment) %>%
mutate(inhibition_range = list(get_range(inhibition))) %>%
unnest() %>%
filter(inhibition <= upper &
inhibition >= lower) %>%
ungroup()
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
pyraclostrobin.plug.discs.filtered %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$inhibition)))

# transforming to log
pyraclostrobin.plug.discs.filtered.2 <-
pyraclostrobin.plug.discs.filtered %>%
mutate(log.inhibition = log(inhibition))
###
## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
pyraclostrobin.plug.discs.filtered.2 %>%
group_by(experimental_replicate) %>%
do(tidy(shapiro.test(.$log.inhibition)))


# no parametric test between experimental repeatlicates and experiment, there is differenc between experiment and experimental replicates, so I cant join data from experimental replicates

pyraclostrobin.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experimental_replicate,
data = .)


pyraclostrobin.plug.discs.filtered  %>%
kruskal.test(inhibition ~ experiment,
data = .)

# Now Dunn test

pyraclostrobin.plug.discs.filtered  %>% DunnTest(inhibition ~ experiment, data = ., method = "bonferroni")
#P VALUE 0.000000000000079 *** plug-paper

```
## Thiophanate_methyl
```{r Thiophanate_methyl}

TM.plug.discs <-
  plug.discs %>% filter(Fungicide == "thiophanate_methyl") %>%
  rename(response = fungicide) %>%
  select(-Fungicide)
  
  TM.plug.discs.filtered <-  TM.plug.discs %>%
  group_by(ID, experiment) %>%
  mutate(response_range = list(get_range(response))) %>%
  unnest() %>%
  mutate(control_range = list(get_range(control))) %>%
  unnest() %>%
  filter(response <= upper &
  response >= lower,
  control <= upper1 & control >= lower1) %>%
  ungroup() %>%
  select(c(ID, experiment,  experimental_replicate, rep, response, control)) %>%
  
  # Percent inhibition is (control - funcide) / (control)
  mutate(inhibition = 100 * ((control - response) / control)) %>%
  #taking again outliers based on inhibition
  group_by(ID, experiment) %>%
  mutate(inhibition_range = list(get_range(inhibition))) %>%
  unnest() %>%
  filter(inhibition <= upper &
  inhibition >= lower) %>%
  ungroup()
  ## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
  TM.plug.discs.filtered %>%
  group_by(experimental_replicate) %>%
  do(tidy(shapiro.test(.$inhibition)))
  
  # transforming to square
  TM.plug.discs.filtered.2 <-  TM.plug.discs.filtered %>%
  mutate(square.inhibition = inhibition ^ 2)
  ###
  ## shapiro test for normality between groups of experimental replicates. There are no normality between experimental replicates
  TM.plug.discs.filtered.2 %>%
  group_by(experimental_replicate) %>%
  do(tidy(shapiro.test(.$square.inhibition)))
  
  
  # non parametric test between experimental repeatlicates and experiment, there is differenc between experiment and no between experimental replicates, so I can join data from experimental replicates
  
  TM.plug.discs.filtered  %>%
  kruskal.test(inhibition ~ experimental_replicate,
  data = .)
  
  
  TM.plug.discs.filtered  %>%
  kruskal.test(inhibition ~ experiment,
  data = .)
  
  # Now Dunn test
  
  TM.plug.discs.filtered  %>% DunnTest(inhibition ~ experiment, data = ., method = "bonferroni")
  #P VALUE 0.0456 * plug-paper
  
```


